Estimating the magnetization distribution within rectangular rock samples

### 2016-06-18 manuscript/manuscript.tex
rerun the validation test by considering the active area of the sensor and also include the respective modifications in the text

We have applied our method to invert the synthetic data produced
by a simulated rock sample (not shown) with $L_{x} = 16$~mm and 
$L_{y} = L_{z} = 3$~mm, according to the Figure \ref{fig:sample}.
This synthetic sample is formed by $P = 16$ juxtaposed prisms along 
the $x$-axis, where each prism has a uniform and high magnetization
(red dots in Figures \ref{fig:estimate-validation},
\ref{fig:estimate-pre-processing} and \ref{fig:estimate-sensor2sample}).
In all tests presented in this section, 
the magnetic data produced by the synthetic sample on 
each plane $\alpha$, $\alpha = 0, 1, 2, 3$, were calculated on
a regular grid of $102 \times 42$ points along the $x$ and 
$y$/$z$ axes, respectively, and were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $30,000$~$\mu$T. These data simulate
an observed data set.
Besides, we have simulated the misalignment problems 
described in the subsection \ref{subsec:Pre-processing}.
Table \ref{tab:misalignment-parameters} shows the parameters
$\theta$, $\Delta x^{\prime}$ and $\Delta y^{\prime}$ (Figure 
\ref{fig:acquisition_errors}b) representing these misalignments
in the magnetic data produced by the synthetic sample on
the planes $\alpha = 0, 1, 2, 3$.

@@

The internal magnetization distribution of our simulated sample
is based on the real magnetization distribution within the
ferro-manganese crust presented by \citet{oda2011}.
Our sample (not shown) is formed by $P = 24$ juxtaposed prisms along the 
$x$-axis and has side 
lengths equal to $L_{x} = 36$~mm, $L_{y} = 5$~mm and $L_{z} = 5$~mm along, 
respectively, the $x$, $y$ and $z$ axes.
Figure \ref{fig:estimate-oda} shows the magnetization of these prisms 
(red dots) along the $x$-axis of the sample.
We have also simulated the presence of $20$ magnetized grains that 
are randomly placed within the sample.
These grains are represented by spheres having radius equal to $30$~$\mu$m,
constant magnetization intensity of $100$~A/m and random magnetization direction.
The magnetic data produced by our heterogeneous sample on 
each plane $\alpha = 0, 1, 2, 3$ were calculated at a
constant distance $h = 370$~$\mu$m, on
a regular grid of $200 \times 100$ points along the $x$ and 
$y$/$z$ axes, respectively, and were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $1.0$~nT (Figures \ref{fig:datafit-oda}a,
d, g and j).

@@

We inverted the observed magnetic data by using an
interpretation model which is formed by $P = 16$ prisms
and has side lengths equal to $L_{x} = 16$~mm, $L_{y} = 3$~mm 
and $L_{z} = 3$~mm along, respectively, the $x$, $y$ and 
$z$ axes.
Note that each prism forming the synthetic sample is 
approximated by four juxtaposed prisms of the 
interpretation model.
Figure \ref{fig:estimate-real} shows the estimated
magnetization distribution obtained with our method.
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-real}b, e, h and k) that recover
the main features in the observed data (Figures \ref{fig:datafit-real}a, 
d, g and j).
This coarse data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-real}c, f, i and l).
These histograms show non-null sample means $\mu$ and 
different sample standard deviations $\sigma$.

>>>>

We have applied our method to invert the synthetic data produced
by a simulated rock sample (not shown) with $L_{x} = 16$~mm and 
$L_{y} = L_{z} = 3$~mm, according to the Figure \ref{fig:sample}.
This synthetic sample is formed by $P = 16$ juxtaposed prisms along 
the $x$-axis, where each prism has a uniform and high magnetization
(red dots in Figures \ref{fig:estimate-validation},
\ref{fig:estimate-pre-processing} and \ref{fig:estimate-sensor2sample}).
In all tests presented in this section, 
the simulated magnetic sensor has an square active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}). Besides,
the magnetic data produced by the synthetic sample on 
each plane $\alpha$, $\alpha = 0, 1, 2, 3$, were calculated on
a regular grid of $102 \times 42$ points along the $x$ and 
$y$/$z$ axes, respectively, and were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $30,000$~$\mu$T. These data simulate
an observed data set.
Besides, we have simulated the misalignment problems 
described in the subsection \ref{subsec:Pre-processing}.
Table \ref{tab:misalignment-parameters} shows the parameters
$\theta$, $\Delta x^{\prime}$ and $\Delta y^{\prime}$ (Figure 
\ref{fig:acquisition_errors}b) representing these misalignments
in the magnetic data produced by the synthetic sample on
the planes $\alpha = 0, 1, 2, 3$.

@@

The internal magnetization distribution of our simulated sample
is based on the real magnetization distribution within the
ferro-manganese crust presented by \citet{oda2011}.
Our sample (not shown) is formed by $P = 24$ juxtaposed prisms along the 
$x$-axis and has side 
lengths equal to $L_{x} = 36$~mm, $L_{y} = 5$~mm and $L_{z} = 5$~mm along, 
respectively, the $x$, $y$ and $z$ axes.
Figure \ref{fig:estimate-oda} shows the magnetization of these prisms 
(red dots) along the $x$-axis of the sample.
We have also simulated the presence of $20$ magnetized grains that 
are randomly placed within the sample.
These grains are represented by spheres having radius equal to $30$~$\mu$m,
constant magnetization intensity of $100$~A/m and random magnetization direction.
The magnetic data produced by our heterogeneous sample on 
each plane $\alpha = 0, 1, 2, 3$ were calculated at a
constant distance $h = 370$~$\mu$m, on
a regular grid of $200 \times 100$ points along the $x$ and 
$y$/$z$ axes, respectively, and were also contaminated with a 
pseudo-random Gaussian noise having null mean and standard 
deviation equal to $1.0$~nT (Figures \ref{fig:datafit-oda}a,
d, g and j).
The simulated magnetic sensor used for calculating these data 
has an square active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}).

@@

We inverted the observed magnetic data by using an
interpretation model which is formed by $P = 16$ prisms
and has side lengths equal to $L_{x} = 16$~mm, $L_{y} = 3$~mm 
and $L_{z} = 3$~mm along, respectively, the $x$, $y$ and 
$z$ axes.
Note that each prism forming the synthetic sample is 
approximated by four juxtaposed prisms of the 
interpretation model.
We considered a square magnetic sensor with active area  
$A = (300 \, \mu \text{m})^{2}$, which was discretized into
a regular grid of $7 \times 7$ points, totalling $Q = 49$
(Figure \ref{fig:b-mag-flux-approx}).
Figure \ref{fig:estimate-real} shows the estimated
magnetization distribution obtained with our method.
This estimated magnetization distribution yields a predicted data
(Figures \ref{fig:datafit-real}b, e, h and k) that recover
the main features in the observed data (Figures \ref{fig:datafit-real}a, 
d, g and j).
This coarse data fit is shown by the normalized histograms of 
the residuals between the predicted and
observed data (Figures \ref{fig:datafit-real}c, f, i and l).
These histograms show non-null sample means $\mu$ and 
different sample standard deviations $\sigma$.
